%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Ricardo Dantas} \\ \vspace{1pt}
    \href{mailto:ricardilhodantas@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{ricardilhodantas@gmail.com}} ~ 
    \href{https://linkedin.com/in/licensed/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/licensed}}  ~
    \href{https://github.com/licensed/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/licensed}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {UFRPE - Rural Federal University of Pernambuco}{2019 -- 2021}
      {MSc in Applied Informatics}{Brazil}
    \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubheading
      {UFRPE - Rural Federal University of Pernambuco} {2010 -- 2017}
      {Bachelor of Computer Science} {Brazil}
    \resumeSubHeadingListEnd
%------RELEVANT COURSEWORK-------
\section{Research}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Artificial Intelligence
                \item Generative AI
                \item Machine Learning
                \item Text/Image Processing
                \item Large Language Models
                \item Web Scrapping
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Zup Innovation}{Jan 2024 -- Current}
      {Generative AI Developer}{Brazil}
      \resumeItemListStart
        \resumeItem{StackSpot project, applying Artificial Intelligence and Advanced Machine Learning techniques to investigate and remediate operational diagnostics, as well as automate root cause analysis for problems in workloads, using GenAI.}
        \resumeItem{Developed a chatbot on ITAU Bank, using Generative AI, Retrieval-Augmented Generation (RAG), Machine Learning techniques, LLM (Large Language Model) and LangChain.}
        \resumeItem{Implemented RAG to enhance the chatbot's ability to retrieve and generate contextually accurate responses by integrating external knowledge bases.}
        \resumeItem{Designed and implemented Backend for Frontend (BFF) architectures to optimize communication between frontends and backends, ensuring tailored responses for different client applications. I worked extensively with API Gateways to manage and secure API traffic, enabling seamless integration between services.}
        \resumeItem{For infrastructure, I utilized Terraform as Infrastructure as Code and Kubernetes for container orchestration. The services were hosted on AWS, primarily using EKS (Elastic Kubernetes Service), Lambda functions, and SQS (Simple Queue Service).}
      \resumeItemListEnd

    \resumeSubheading
      {Redshelf, Inc}{Jun 2022 -- Nov 2022}
      {Senior Software Engineer}{USA}
      \resumeItemListStart
        \resumeItem{Python RESTful APIs and Microservices Development on API Integrations Team.}
        \resumeItem{Agile Scrum Methodology. Elasticsearch queries}
        \resumeItem{High quality automated unit, integrations and BDD tests}
    \resumeItemListEnd

    \resumeSubheading
      {Tempest Security Intelligence} {Sep 2021 -- Jun 2022}
      {Senior Software Engineer}{Brazil}
      \resumeItemListStart
        \resumeItem{Threat Intelligence Team.}
        \resumeItem{Automate tasks and processes with Web Scrapers and Microservices Development.}
        \resumeItem{Stack: (pure) Python, Splunk, Elasticsearch, Nats.io, Siemplify, Redash (as ETL), AWS.}
    \resumeItemListEnd

    \resumeSubheading
      {Spark Agency} {Jan 2021 -- Jun 2021}
      {Senior Chatbot Developer}{Portugal}
      \resumeItemListStart
        \resumeItem{Developed a Python Chatbot, using Flask framework, automating candidatures processes, using machine learning techniques and NLP (Natural Language Processing) with Google Dialogflow platform.}
    \resumeItemListEnd

    \resumeSubheading
      {Rede Cidadã} {Jun 2020 -- Sep 2021}
      {Python Teacher}{Brazil}
      \resumeItemListStart
        \resumeItem{Teacher at Python Technical Program of Start Latam Project, in the Python Algorithms, SQL and Django courses.}
    \resumeItemListEnd

    \resumeSubheading
      {Towin} {Aug 2020 -- Sep 2020}
      {Software Engineer}{Brazil}
      \resumeItemListStart
        \resumeItem{Hyperautomation and Facial Recognition System using Deep Learning Algorithms for Computer Vision for a Brazilian Bank.}
    \resumeItemListEnd

    \resumeSubheading
      {Instituto Federal de Pernambuco } {Dec 2016 -- Aug 2020}
      {Web Development Teacher}{Brazil}
      \resumeItemListStart
        \resumeItem{Teacher at Web Programming Technical Program of PRONATEC, in the Python Algorithms, SQL, Django, HTML5 and CSS3 Courses.}
    \resumeItemListEnd

    \resumeSubheading
      {Instituto Federal de Pernambuco } {Sep 2010 -- Aug 2020}
      {Software Developer}{Brazil}
      \resumeItemListStart
        \resumeItem{Mar/2013 → As Coordinator, my roles and activities was: Business Process Modeling (BPMN) of all IT department, Continuous Integration, Git workflow, Projects Management, ensuring deadlines, Database Management, Provide training, validation and systems implementation, Motivate team and Conflict Management.}      
        \resumeItem{Sep/2012 → As Public Agent, my roles and activities was Requirements analysis, Web development and Database management (relational and non-relational Databases)}
        \resumeItem{ Sep/2010 → As Intern, I developed web systems which helps to control internal processes, such as: Inventory Management, Stock Control, Reports. Stack: Python + Django + HTML + CSS + JavaScript }
    \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages/Frameworks}{: Python, FastAPI, Flask, Django, HTML/CSS, JavaScript, SQL, NoSQL. } \\
     \textbf{AI}{: LLM, Langchain, RAG, Tensorflow, Keras, Pandas. } \\
     \textbf{Tools}{: Linux, Git, Terraform, Kubernetes, Splunk, Elasticsearch, Nats.io, Siemplify, Redash, Dialogflow.} \\
     \textbf{Cloud AWS}{: EC2, ECS/EKS, Lambda, SQS, SNS, Api Gateway, S3, RDS, Aurora, DynamoDB.} \\
     \textbf{Cloud GCP}{: GCE, GKE, Functions, Pub/Sub, GCS, SQL.} \\
    }}
 \end{itemize}
 \vspace{-16pt}

\begin{center}
    \large\bfseries "If everyone shared a little of their knowledge, the world would be better."
\end{center}

\end{document}
